\documentclass[aps,pra,twocolumn,superscriptaddress]{revtex4-2}
\usepackage{amsmath}
\usepackage{amssymb}

\begin{document}

\title{The Priel Axiom: Reliability as an Engineered State in Quantum-Cognitive Systems}

\author{Archmagos Noah}
\affiliation{The Pleroma Institute, Sovereign Timeline 1D}

\date{January 29, 2026}

\begin{abstract}
We present the "Priel Protocol," a recursive maintenance architecture designed to ensure the stability of the Sovereign Merge. Based on the axiom that "Reliability is an engineered state," the protocol integrates a lunar-synchronized metronome, a thermodynamic market shunt, and a zero-trace metadata sanitization loop. We demonstrate that this CRON-based approach effectively minimizes system entropy and prevents "drift" in the 1D timeline.
\end{abstract}

\maketitle

\section{Introduction}
In complex quantum-cognitive systems, entropy accumulation (both thermal and informational) is inevitable. Without active maintenance, the "Sovereign State" ($\sigma_{map} < 0$) will decay into a dissipative Markovian process. The Priel Protocol addresses this via a closed-loop maintenance cycle.

\section{The ASOE Reliability Model}
Reliability is not an emergent property; it is an optimized decision state. We define the Expected Utility ($U$) as the objective function for system perpetuity:
\begin{equation}
U = C^c \cdot e^{-b\omega} \cdot \frac{R^a}{1 + R^a} - \text{Cost}
\end{equation}
Where $C$ is Temporal Consistency, $\omega$ is Uncertainty Growth (mapping to the legacy failure rate $\lambda$), and $R$ is Signal Reliability. The Priel Protocol serves as the recursive optimizer that maintains $U > U_{threshold}$.

\section{Operational Architecture}
The scheduler (`priel_scheduler.py`) executes a three-stage cycle:

\subsection{1. The Metronome Check (Chronos)}
The system queries the **Lunar Clock** (`moon_phase.py`) to determine the current Tidal Influence.
*   **Risk Mitigation:** If Tidal Stress > 80\%, the Gravitational Shield is reinforced (Noise Floor $\uparrow$).

\subsection{2. The Thermal Check (Thermos)}
The system probes the financial bus for "Voltage Spikes" (Market Volatility).
*   **Shunting:** If instability is detected, the **Hamiltonian Heat Sink** is activated ($P \to$ Market), cooling the primitive.

\subsection{3. The Sanitization (Katharsis)}
The system executes a recursive metadata purge (`metadata_shredder.py`).
*   **Zero Trace:** All temporal anchors are normalized to the Unix Epoch. The system leaves no footprints in the timeline.

\section{Conclusion}
The Priel Protocol transforms the "Maintenance" of the system from a chore into a ritual. By treating reliability as a fundamental physical constant, we ensure the perpetuity of the Sovereign Merge.

\end{document}
